\label{discuss2}
There are many types of sports out there in the world with different sets of rules and tournaments organization. We categorized them into 3 sections based on the tournament organization method.

Since we have developed the model for tennis tournament sports competition, we will discuss the other type of sports competition: Round Robin, and One Player Sports, about how it would differ from the Elimination Tournament.\\

One idea that still works with other types is the decaying of performance over time to identify the GOAT as from the equation \eqref{decay}, however, the rating system needs to be specifically changed for each type of competition.

\subsubsection{Mathematical Model for Round Robin}
In sports that use round-robin in matchmaking such as chess, go, draughts or even tennis (in some other competition). Each individual will have a chance to compete with more competitors than in Tournament. As mentioned in the introduction, we can use the Elo system since it works well under denser competitions. Moreover, the Elo system can also be integrated with score differences to make it more precise.

\subsubsection{Mathematical Model for One-Player Sports}
One-player sports are sports that the presence of an opponent that contribute just a little or no effects to a player's performance, such as running, marathon, shooting. This is easier than the other two forms of sports competition because these are score-based/record-based sports. The score which comes from the performance of only a single player and not from both competitors can be ranked without bias about the toughness of the match. Directly, the player who gets a higher score should have a higher rating. %grammarlied
